Notes on the low density parameters in {\tt MAESTRO}

### 2009-09-16 docs/lo_density/lo_density.tex
updated figure
we trigger the point where we turn off psi using base_cutoff_density rather than anelastic_cutoff_density.  now all parameters relevant to multilevel paper, except for div_coeff, cut off base_cutoff_density
typo

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff}.
We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption{Image of how the cutoff density and cutoff coordinates
are related.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt anelastic\_cutoff\_coord}$.
  \MarginPar{I think we want to change this to $r \le {\tt anelastic\_cutoff\_coord}$.}

@@

>>>>

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff}.
We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption{Image of how the cutoff density and cutoff coordinates
are related.  This is drawn assuming {\tt drdxfac}=5.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt base\_cutoff\_density\_coord}$.
  \MarginPar{I think we want to change this to $r \le {\tt base\_cutoff\_density\_coord}$.}
